Supplemental data to ``\emph{k}-mer-based GWAS enhances causal variant and candidate gene discovery in soybean''

### 2023-02-28 additional_files/additional_file_1.tex
Integrate suggestions by JA Sibbesen into the supplemental results

This section provides a more detailed account of some the the results obtained
by the GWAS analyses on a per-trait basis. Aspects of the results that were
already discussed in the main text are not repeated here; in such cases,
readers are simply redirected to specific tables and figures containing
detailed results from all four GWAS approaches. A summary of the signals found
at all loci using all four methods is presented in Table \ref{signals_table}.
Readers are invited to refer to this table as we go over the results obtained
for each trait below.

@@

We conducted a single GWAS analysis contrasting purple and white flower colors
(Table \ref{FLOWER.COLOR_gwas_table}). Of the two classical loci reported by
\cite{bandillo2017}, \textit{W1} was detected by all four GWAS approaches whereas
\textit{L1} was detected by none of the approaches (Figure
\ref{flower_color_manhattan}). These results are unsurprising as W1 is the
major contributor to flower color in soybean, whereas the \textit{L1} locus
(typically associated with pod color) was detected with a much less significant
\textit{p}-value (see Table \ref{signals_table}) and only conjectured as
associated with flower color by \cite{bandillo2017}. Detailed results for the
\textit{W1} locus can be viewed in figures \ref{flower-color-main-figure},
\ref{flower_color_W1_signal} and \ref{flower_color_W1_gene}.

The \textit{k}-mer GWAS analysis also identified presumably spurious significant
\textit{k}-mers scattered throughout the genome (Figure
\ref{flower_color_manhattan}). An analysis of the pairwise LD between a subset
of those \textit{k}-mers showed that all \textit{k}-mers formed a single LD block
linked to the \textit{W1} locus (Figure \ref{flower_color_ld}), ruling out the
presence of a second locus controlling that trait in this population.

@@

We conducted two GWAS analyses on pubescence color. The first analysis
contrasted gray, tawny and light tawny pubescence colors (Table
\ref{PUBESCENCE.COLOR_gwas_table}) and detected a signal overlapping the
\emph{T} locus using all four approaches (Figure
\ref{pubescence_color_all_manhattan}). Detailed results at the \textit{T} locus
van be viewed in figures \ref{pubescence_color_all_T_signal},
\ref{pubescence_color_all_T_gene} and \ref{pubescence_color_all_T_kmers}. We
observed that not all accessions with gray pubescence harbored the deleted
nucleotide, which could indicate either that other causal variants resulting in
a non-functional F3’H are present in this population, or that the causal
variant lies elsewhere.

@@

The second GWAS analysis on seed coat color focused on a subset of accessions
with yellow or green seed coat only, as this difference is controlled by the
\emph{G} locus (Table \ref{SEED.COAT.COLOR_gwas_table}). Detailed results of
this analysis can be viewed in figures \ref{seed-coat-color-main-figure},
\ref{seed_coat_color_greenyellow_manhattan},
\ref{seed_coat_color_greenyellow_G_signal} and
\ref{seed_coat_color_greenyellow_G_gene}.

@@

We conducted two GWAS analyses on stem termination type. The first GWAS
included all phenotypes observed in the dataset (determinate, semi-determinate,
and indeterminate; Table \ref{STEM.TERMINATION.TYPE_gwas_table}). The results
of this analysis and the \textit{Dt1} locus can be viewed in figures \ref{stem_termination_all_manhattan}
\ref{stem_termination_all_Dt1_signal}, \ref{stem_termination_all_Dt1_gene} and
\ref{stem_termination_all_Dt1_kmers}.

The second GWAS analysis that we conducted on this trait included only
semi-determinate and indeterminate phenotypes in an attempt to detect signals
at the \emph{Dt2} locus (Table \ref{STEM.TERMINATION.TYPE_gwas_table}).
However, this was unsuccessful using all four GWAS
approaches (Figure \ref{stem_termination_sn_manhattan}). Similarly, we failed to
detect signals at the \textit{E3} locus, which is more commonly associated
with maturity but was mentioned as associated with stem termination type by
\cite{bandillo2017}.

@@

We conducted three different GWAS analyses on hilum color. The first GWAS
included seven colors (Table \ref{HILUM.COLOR_gwas_table}) and detected signals
at the \emph{I}, \emph{T} and \emph{R} loci using all four approaches except vg
at the \emph{R} locus (Figure \ref{hilum_color_all_manhattan}) while no signals
were detected at the \emph{O} and \emph{W1} loci studied by
\cite{bandillo2017}. The detailed results for the \textit{I} locus can be viewed
in figure \ref{hilum_color_all_I_signal} whereas those for the \textit{T} locus
can be viewed in figures \ref{hilum_color_all_T_signal}, \ref{hilum_color_all_T_gene}
and \ref{hilum_color_all_T_kmers}.

@@

A second GWAS analysis contrasting accessions with either black or brown hilum
color was better suited at resolving the signal at the \emph{R} locus (Table
\ref{HILUM.COLOR_gwas_table}). Accordingly, this GWAS analysis detected strong
signals overlapping the \emph{R} locus and no other classical loci using all
four approaches (Figure \ref{hilum_color_blackbrown_manhattan}).
\cite{gillman2011} identified the R2R3 MYB transcription factor Glyma.09g235100
as the molecular basis for the \emph{R} locus and documented four different
loss-of-function alleles linked to brown hilum color. Although our analyses did
detect strong signals in the vicinity of this gene, the most associated markers
were not located in the body of the gene (Figure
\ref{hilum_color_blackbrown_R_signal}). Interestingly, the most significantly
associated \emph{k}-mers detected by our analysis mapped 2 kb upstream of
another gene (Glyma.09g234900) annotated as a MYB transcription factor and
putatively involved in the regulation of anthocyanin biosynthesis. This gene
as well as Glyma.09g235100 and two others are part of a tandem array of four
R2R3 MYB genes considered candidates by \cite{gillman2011}, and of which
Glyma.09g235100 was the only one expressed in the seed coat. Given the
convincing evidence provided by \cite{gillman2011}, it is most likely that
Glyma.09g235100 is indeed the gene associated with the \emph{R} locus and that
our failure to identify the most significantly associated \emph{k}-mers as
causal variants is due to the coexistence of several variants that can cause
loss of function at the \emph{R} locus. Indeed, we observed at least two causal
variants (a 1-bp deletion and a SNP) previously documented by
\cite{gillman2011} in our dataset (Figure \ref{hilum_color_blackbrown_R_gene},
\ref{hilum_color_blackbrown_R_kmers}), although they were not among the most
significantly associated markers or \emph{k}-mers.

@@

We conducted two GWAS analyses on pod color. The first analysis included four
different colors (Table \ref{POD.COLOR_gwas_table}) and resulted in the
detection of signals overlapping both the \emph{L1} and \emph{L2} loci with all
four methods (Figure \ref{pod_color_all_manhattan}). Detailed results at the
\textit{L1} locus can be viewed in figure \ref{pod_color_all_L1_signal},
whereas detailed results at the \textit{L2} locus can be viewed in figure
\ref{pod_color_all_L2_signal}.

The second GWAS contrasted black and brown pods with the objective of detecting
signals that provided better resolution at the \emph{L1} locus (Table
\ref{POD.COLOR_gwas_table}).  Accordingly, all four methods detected a signal
at the \emph{L1} locus but not at the \emph{L2} locus using this GWAS (Figure
\ref{pod_color_blbr_manhattan}).  Results at the \emph{L1} locus were similar
to those observed when using all observed phenotypes, but the \emph{k}-mer
analysis revealed a previously undocumented signal on chromosome Gm15 which was
not in LD with any other signal (Figures \ref{pod_color_blbr_manhattan},
\ref{pod_color_blbr_ld}). The observed signal at this locus overlaps a total of
27 genes (Figure \ref{pod_color_blbr_pdcGm15_signal}), but none of those was
annotated as having an obvious role in controlling pod color.

@@

We conducted two different GWAS on pubescence form. The first GWAS used three
phenotypes (erect, semi-appressed and appressed; Table
\ref{PUBESCENCE.FORM_gwas_table}) and detected signals overlapping the
\emph{Pa1} locus using all four approaches as well as signals overlapping the
\emph{Pa2} locus using Platypus and the \emph{k}-mer approaches (Figure
\ref{pubescence_form_all_manhattan}). Detailed results at the \textit{Pa1} locus
can be viewed in figure \ref{pubescence_form_all_Pa1_signal},
\ref{pubescence_form_all_Pa1_gene} and \ref{pubescence_form_all_Pa1_kmers},
whereas detailed results at the \textit{Pa2} locus can be viewed in figure
\ref{pubescence_form_all_Pa2_signal}.

@@

A second GWAS analysis focused only on appressed and semi-appressed phenotypes
with the objective of enhancing the signal at the \emph{Pa2} locus. However,
this analysis only detected weak signals at the \emph{Pa1} locus (Figure
\ref{pubescence_form_noerect_manhattan}) and its results were therefore not
analyzed further.

@@

We conducted a single GWAS analysis on pubescence density (Table
\ref{PUBESCENCE.DENSITY_gwas_table}), which detected signals at the \emph{Ps}
locus but not the \emph{Pd1} and \emph{P1} loci using all four approaches
(Figure \ref{pubescence_density_manhattan}). \cite{liu2020ps} linked the gene
Glyma.12g187200 to the \emph{Ps} locus and identified copy number variation
(CNV) of a 25.6-kb sequence including this gene as the causal variant, with
higher copy number resulting in decreased pubescence. Through a segmentation
analysis of the sequencing depth in accessions with increased copy number, we
identified the boundaries of the region varying in copy number as 36,254,989 -
36,297,368 on chromosome Gm12 of genome assembly version 4 of Williams82, for a
total of about 42 kb. Detailed results at this locus can be viewed in figures
\ref{pubescence_density_Ps_signal}, \ref{pubescence_density_Ps_gene}, and
\ref{pubescence-density-main-figure}.

@@

We performed three different GWAS analyses on seed coat luster (Table
\ref{SEED.COAT.LUSTER_gwas_table}).  However, all three yielded similar results
(Figure \ref{seed_coat_luster_all_manhattan},
\ref{seed_coat_luster_nointermediate_manhattan},
\ref{seed_coat_luster_dullshiny_manhattan}) so we chose to focus on the
analysis contrasting the dull and shiny phenotypes as it yielded the most
significant signals and also provided the most consistent results in the
analysis previously done by \cite{bandillo2017}. This analysis detected
signals at the \emph{B} locus as the sole classical locus using all four
methods (Figure \ref{seed_coat_luster_dullshiny_manhattan}). Apparent signals
on chromosomes Gm20 and Gm09 (which may correspond to the B? locus reported by
\cite{bandillo2017}) were also detected, but analysis of the LD patterns
between \emph{k}-mers suggested that these signals were most likely in LD with
the \emph{B} locus (Figure \ref{seed_coat_luster_dullshiny_ld}). All methods
also detected signals overlapping the \emph{Hps} locus as defined by
\cite{bandillo2017}, however results shown in \cite{gijzen2003} and our results
suggest that \emph{Hps} and \emph{B} are the same locus. Using a segmentation analysis
similar to the one used for the \emph{Ps} locus, we identified a 31-kb region
spanning positions 9,386,109-9,417,431 on chromosome Gm15 that exhibited
variation in copy number across accessions and overlapped four genes annotated
as containing HPS domains (Figures \ref{seed_coat_luster_dullshiny_B_signal},
\ref{seed_coat_luster_dullshiny_B_gene}). The top 5\% / 1\% significant
associations of all approaches other than vg overlapped this CNV region and the
most significantly associated \emph{k}-mer was located within the CNV region
(Figures \ref{seed_coat_luster_dullshiny_B_signal},
\ref{seed_coat_luster_dullshiny_B_gene}), however we were not able to link any
of the variants found to the presence of copy number variation.

@@

A GWAS conducted on maturity group did not yield any significant signals
overlapping the classical E1-E4 loci using any of the four GWAS approaches,
although signals at the E1 locus did approach significance in the Platypus
analysis (Table \ref{MATURITY.GROUP_gwas_table}, Figure \ref{maturity_group_manhattan}).

@@

We conducted a single GWAS analysis on horizontal resistance to
\textit{Phytophthora sojae} using corrected dry weight (CDW) as a quantitative
measure of resistance. Detailed results can be viewed in figures
\ref{corrected_dry_weight_manhattan} and
\ref{corrected_dry_weight_cdwGm15_signal}.

@@

We conducted a GWAS analysis on the seed oil content data obtained from the
GRIN database. While several seed oil content quantitative trait loci (QTL)
have been reported due to high interest in this trait for soybean breeding
\citep{chaudhary2015}, we focused on two major QTL on chromosomes Gm15 and Gm20
that have often been reported in \emph{G. max}, and notably observed by
\cite{bandillo2015} on a collection of USDA lines using SoySNP50K chip
genotypes and GRIN phenotypic data. We identified a signal located on
chromosome Gm15 using the \emph{k}-mer approach only (Figure
\ref{oil_manhattan}). Although this signal did not overlap with the coordinates
found by \cite{bandillo2017}, it was located only 2 kb away from it and 30 kb
away from Glyma.15g049200, the sugar transporter gene identified by
\cite{zhang2020} as associated with that locus. Therefore, the significantly
associated \emph{k}-mers were not linked to the causal variation at that locus.

@@

Similarly to seed oil content, we conducted a GWAS on seed protein content
using data obtained from the GRIN database. As is generally the case in
soybean given the negative correlation between seed oil and protein content,
the two major QTL considered above and reported by \cite{bandillo2015} for seed
oil content are also major QTL for seed protein content. We identified a signal
at the locus located on chromosome Gm20 only, and only using the genotypes
called by vg (Figure \ref{protein_manhattan}). However, the SV discovered as
significantly associated was located about 700 kb from the gene cloned by
\cite{fliege2022} for that locus (Glyma.20g085100) and therefore is unlikely to
represent the causal variation at that locus.

>>>>

This section provides a more detailed per-trait account of some of the results obtained
by the GWAS analyses. Aspects of the results that were
already discussed in the main text are not repeated here; in such cases,
readers are simply redirected to specific tables and figures containing
detailed results from all four GWAS approaches. A summary of the signals found
at all loci using all four methods is presented in Table \ref{signals_table}.

@@

We conducted a GWAS analysis contrasting purple and white flower colors
(Table \ref{FLOWER.COLOR_gwas_table}). Of the two classical loci reported by
\cite{bandillo2017}, \textit{W1} was detected by all four GWAS approaches whereas
\textit{L1} was detected by none of the approaches (Figure
\ref{flower_color_manhattan}). These results are unsurprising as W1 is the
major contributor to flower color in soybean, whereas the \textit{L1} locus
(typically associated with pod color) was detected with a much less significant
\textit{p}-value (see Table \ref{signals_table}) and only conjectured as
associated with flower color by \cite{bandillo2017}. Detailed results for the
\textit{W1} locus can be viewed in figures \ref{flower-color-main-figure},
\ref{flower_color_W1_signal} and \ref{flower_color_W1_gene}.

The \textit{k}-mer GWAS analysis also identified presumably spurious significant
\textit{k}-mers scattered throughout the genome (Figure
\ref{flower_color_manhattan}). An analysis of the pairwise LD between a subset
of those \textit{k}-mers showed that most \textit{k}-mers formed a single LD block
linked to the \textit{W1} locus (Figure \ref{flower_color_ld}). A small LD block
occurred on chromosome Gm09, however it was in moderate LD with the one on chromosome
Gm13 and therefore probably does not represent a separate locus.

@@

We conducted two different GWAS analyses on pubescence color. The first analysis
contrasted gray, tawny and light tawny pubescence colors (Table
\ref{PUBESCENCE.COLOR_gwas_table}) and detected a signal overlapping the
\emph{T} locus using all four approaches (Figure
\ref{pubescence_color_all_manhattan}). Detailed results at the \textit{T} locus
can be viewed in figures \ref{pubescence_color_all_T_signal},
\ref{pubescence_color_all_T_gene} and \ref{pubescence_color_all_T_kmers}. We
observed that not all accessions with gray pubescence harbored the deleted
nucleotide, which could indicate either that other causal variants are resulting in
a non-functional F3’H in this population, or that the causal
variant lies elsewhere.

@@

The second GWAS analysis on seed coat color focused on the subset of accessions
with yellow or green seed coat only (Table \ref{SEED.COAT.COLOR_gwas_table}),
as this difference is controlled by the \emph{G} locus. Detailed results of
this analysis can be viewed in figures \ref{seed-coat-color-main-figure},
\ref{seed_coat_color_greenyellow_manhattan},
\ref{seed_coat_color_greenyellow_G_signal} and
\ref{seed_coat_color_greenyellow_G_gene}.

@@

We conducted two different GWAS analyses on stem termination type. The first GWAS
included all phenotypes observed in the dataset (determinate, semi-determinate,
and indeterminate; Table \ref{STEM.TERMINATION.TYPE_gwas_table}). The results
of this analysis at the \textit{Dt1} locus can be viewed in figures \ref{stem_termination_all_manhattan},
\ref{stem_termination_all_Dt1_signal}, \ref{stem_termination_all_Dt1_gene} and
\ref{stem_termination_all_Dt1_kmers}.

The second GWAS analysis included only
semi-determinate and indeterminate phenotypes. We performed this analysis in an attempt to also detect signals
at the \emph{Dt2} locus (Table \ref{STEM.TERMINATION.TYPE_gwas_table}).
However, this was unsuccessful using all four GWAS
approaches (Figure \ref{stem_termination_sn_manhattan}). Similarly, we failed to
detect signals at the \textit{E3} locus, which is more commonly associated
with maturity but was mentioned as associated with stem termination type by
\cite{bandillo2017}.

@@

We conducted three different GWAS analyses on hilum color. The first GWAS
included seven colors (Table \ref{HILUM.COLOR_gwas_table}) and detected signals
at the \emph{I}, \emph{T} and \emph{R} loci using all four approaches except vg
at the \emph{R} locus (Figure \ref{hilum_color_all_manhattan}). No signals
were detected at the \emph{W1} and \emph{O} loci studied by
\cite{bandillo2017}. The detailed results for the \textit{I} locus can be viewed
in figure \ref{hilum_color_all_I_signal} whereas those for the \textit{T} locus
can be viewed in figures \ref{hilum_color_all_T_signal}, \ref{hilum_color_all_T_gene}
and \ref{hilum_color_all_T_kmers}.

@@

The second GWAS analysis contrasting accessions with either black or brown hilum
color was better suited at resolving the signal at the \emph{R} locus (Table
\ref{HILUM.COLOR_gwas_table}). Accordingly, this GWAS analysis detected strong
signals overlapping the \emph{R} locus and no other classical loci using all
four approaches (Figure \ref{hilum_color_blackbrown_manhattan}).
\cite{gillman2011} identified the R2R3 MYB transcription factor Glyma.09g235100
as the molecular basis for the \emph{R} locus and documented four different
loss-of-function alleles linked to brown hilum color. Although our analyses did
detect strong signals in the vicinity of this gene, the most associated markers
were not located in the body of the gene (Figure
\ref{hilum_color_blackbrown_R_signal}). Interestingly, the most significantly
associated \emph{k}-mers detected by our analysis mapped 2 kb upstream of
another gene (Glyma.09g234900) annotated as a MYB transcription factor and
putatively involved in the regulation of anthocyanin biosynthesis. This gene
as well as Glyma.09g235100 and two others are part of a tandem array of four
R2R3 MYB genes considered as candidates by \cite{gillman2011}, and of which
Glyma.09g235100 was the only one expressed in the seed coat. Given the
convincing evidence provided by \cite{gillman2011}, it is most likely that
Glyma.09g235100 is indeed the gene associated with the \emph{R} locus and that
our failure to identify the most significantly associated \emph{k}-mers as
causal variants is due to the coexistence of several variants that can cause
loss of function at the \emph{R} locus. Indeed, we observed at least two causal
variants (a 1-bp deletion and a SNP) previously documented by
\cite{gillman2011} in our dataset (Figure \ref{hilum_color_blackbrown_R_gene},
\ref{hilum_color_blackbrown_R_kmers}).

@@

We conducted two different GWAS analyses on pod color. The first analysis included four
different colors (Table \ref{POD.COLOR_gwas_table}) and resulted in the
detection of signals overlapping both the \emph{L1} and \emph{L2} loci using all
four methods (Figure \ref{pod_color_all_manhattan}). Detailed results at the
\textit{L1} locus can be viewed in figure \ref{pod_color_all_L1_signal},
whereas detailed results at the \textit{L2} locus can be viewed in figure
\ref{pod_color_all_L2_signal}.

The second GWAS analysis compared black and brown pods with the objective of detecting stronger
signals at the \emph{L1} locus (Table
\ref{POD.COLOR_gwas_table}).  Accordingly, all four methods detected a signal
at the \emph{L1} locus but not at the \emph{L2} locus using this GWAS (Figure
\ref{pod_color_blbr_manhattan}).  Results at the \emph{L1} locus were similar
to those observed when using all observed phenotypes, but the \emph{k}-mer
analysis revealed a previously undocumented signal on chromosome Gm15 which was
not in LD with any other signal (Figures \ref{pod_color_blbr_manhattan},
\ref{pod_color_blbr_ld}). The observed signal at this locus overlaps a total of
27 genes (Figure \ref{pod_color_blbr_pdcGm15_signal}), but none of those are
annotated as having an obvious role in controlling pod color.

@@

We conducted two different GWAS analyses on pubescence form. The first analysis used three
phenotypes (erect, semi-appressed and appressed; Table
\ref{PUBESCENCE.FORM_gwas_table}) and detected signals overlapping the
\emph{Pa1} locus using all four approaches as well as signals overlapping the
\emph{Pa2} locus using Platypus and the \emph{k}-mer approach (Figure
\ref{pubescence_form_all_manhattan}). Detailed results at the \textit{Pa1} locus
can be viewed in figure \ref{pubescence_form_all_Pa1_signal},
\ref{pubescence_form_all_Pa1_gene} and \ref{pubescence_form_all_Pa1_kmers},
whereas results at the \textit{Pa2} locus can be viewed in figure
\ref{pubescence_form_all_Pa2_signal}.

@@

The second GWAS analysis focused only on appressed and semi-appressed phenotypes
with the objective of enhancing the signal at the \emph{Pa2} locus. However,
this analysis only detected weak signals at the \emph{Pa1} locus (Figure
\ref{pubescence_form_noerect_manhattan}) and its results were therefore not
analyzed further.

@@

We conducted a GWAS analysis on pubescence density (Table
\ref{PUBESCENCE.DENSITY_gwas_table}), which detected signals at the \emph{Ps}
locus but not the \emph{Pd1} and \emph{P1} loci using all four approaches
(Figure \ref{pubescence_density_manhattan}). \cite{liu2020ps} linked the gene
Glyma.12g187200 to the \emph{Ps} locus and identified ia 25.6-kb copy number variation
containing this gene as the causal variant, with
higher copy number resulting in decreased pubescence. By
analyzing the sequencing depth in accessions with increased copy number, we
identified the boundaries of the CNV region as 36,254,989 -
36,297,368 (42 kb) on chromosome Gm12.
Detailed results at this locus can be viewed in figures \ref{pubescence-density-main-figure},
\ref{pubescence_density_Ps_signal} and \ref{pubescence_density_Ps_gene}.

@@

We performed three different GWAS analyses on seed coat luster (Table
\ref{SEED.COAT.LUSTER_gwas_table}). Since all three analyses yielded similar results
(Figure \ref{seed_coat_luster_all_manhattan},
\ref{seed_coat_luster_nointermediate_manhattan},
\ref{seed_coat_luster_dullshiny_manhattan}), we chose to focus on the
GWAS contrasting the dull and shiny phenotypes as it yielded the most
significant signals. In addition, it also provided results that were most consistent with the
analysis previously done by \cite{bandillo2017}. The analysis detected
signals at the \emph{B} locus as the sole classical locus using all four
methods (Figure \ref{seed_coat_luster_dullshiny_manhattan}). Apparent signals
on chromosomes Gm20 and Gm09 (which may correspond to the B? locus reported by
\cite{bandillo2017}) were also detected, but analysis of the LD patterns
between \emph{k}-mers suggested that these signals were most likely in LD with
the \emph{B} locus (Figure \ref{seed_coat_luster_dullshiny_ld}). All methods
also detected signals overlapping the \emph{Hps} locus as defined by
\cite{bandillo2017}, however results shown by \cite{gijzen2003} and our results
suggest that \emph{Hps} and \emph{B} are the same locus. Using a sequencing depth-based segmentation analysis
similar to the one used for the \emph{Ps} locus, we identified a 31-kb region
spanning positions 9,386,109-9,417,431 on chromosome Gm15 that exhibited
variation in copy number across accessions and overlapped four genes annotated
as containing HPS domains (Figures \ref{seed_coat_luster_dullshiny_B_signal},
\ref{seed_coat_luster_dullshiny_B_gene}). The top 5\% / 1\% significant
associations of all approaches other than vg overlapped this CNV region and the
most significantly associated \emph{k}-mer was located within the CNV region
(Figures \ref{seed_coat_luster_dullshiny_B_signal},
\ref{seed_coat_luster_dullshiny_B_gene}). However we were not able to link any
of the variants found to the presence of copy number variation.

@@

We conducted on a GWAS analysis on maturity group which did not yield any significant signals
overlapping the classical E1-E4 loci using any of the four GWAS approaches.
However, signals at the E1 locus did approach significance in the Platypus
analysis (Table \ref{MATURITY.GROUP_gwas_table}, Figure \ref{maturity_group_manhattan}).

@@

We conducted a GWAS analysis on horizontal resistance to
\textit{Phytophthora sojae} using corrected dry weight (CDW) as a quantitative
measure of resistance. Detailed results can be viewed in figures
\ref{corrected_dry_weight_manhattan} and
\ref{corrected_dry_weight_cdwGm15_signal}.

@@

We conducted a GWAS analysis on seed oil content using data obtained from the
GRIN database. While several seed oil content quantitative trait loci (QTL)
have been reported due to high interest in this trait for soybean breeding
\citep{chaudhary2015}, we focused on two major QTL on chromosomes Gm15 and Gm20.
These loci have often been reported in \emph{G. max} and were notably observed by
\cite{bandillo2015} on a collection of USDA lines using SoySNP50K chip
genotypes and GRIN phenotypic data. We identified a signal located on
chromosome Gm15 using the \emph{k}-mer approach only (Figure
\ref{oil_manhattan}). Although this signal did not overlap with the coordinates
found by \cite{bandillo2017}, it was located only 2 kb away from it and 30 kb
away from Glyma.15g049200, the sugar transporter gene identified by
\cite{zhang2020} as associated with that locus. Therefore, the significantly
associated \emph{k}-mers were not linked to the causal variation at that locus.

@@

Similarly to seed oil content, we conducted a GWAS on seed protein content
using data obtained from the GRIN database. As is generally the case in
soybean given the negative correlation between seed oil and protein content,
the two major QTL considered above and reported by \cite{bandillo2015} for seed
oil content are also major QTL for seed protein content. We only identified a signal
at the locus located on chromosome Gm20, and only using the genotypes
called by vg (Figure \ref{protein_manhattan}). However, the SV discovered as
significantly associated was located about 700 kb from the gene cloned by
\cite{fliege2022} for that locus (Glyma.20g085100). It is therefore unlikely that this SV
represents the causal variation at that locus.
